Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-17 paper/main.tex
minor tweaks to intro

\section*{Introduction}
Engaging in physical activity (exercise) can improve our physical
fitness by increasing muscle strength~\citep{RogeEvan93, Lind79,
  CranEtal13, Knut07}, increasing bone density~\citep{ChilEtal12,
  BassRams94, LaynNels99}, increasing cardiovascular
performance~\citep{MaioEtal00, PollEtal00}, increasing lung
capacity~\citep{LazoEtal16}~\citep[although see][]{RomaEtal16},
increasing endurance~\citep{WilmKnut03}, and more.  Exercise can also
improve mental health~\citep{Ragl90, MikkEtal17, TaylEtal85,
  DeslEtal09, Call04, PaluSchw00} and cognitive performance~\citep{ChanEtal12b,
  BrisEtal02, EtniEtal06}.

>>>>

\section*{Introduction}
Engaging in physical activity (exercise) can improve our physical
fitness by increasing muscle strength~\citep{RogeEvan93, Lind79,
  CranEtal13, Knut07}, increasing bone density~\citep{ChilEtal12,
  BassRams94, LaynNels99}, increasing cardiovascular
performance~\citep{MaioEtal00, PollEtal00}, increasing lung
capacity~\citep{LazoEtal16}~\citep[although see][]{RomaEtal16},
increasing endurance~\citep{WilmKnut03}, and more.  Exercise can also
improve mental health~\citep{Ragl90, MikkEtal17, TaylEtal85,
  DeslEtal09, Call04, PaluSchw00, BassSuzu17} and cognitive performance~\citep{ChanEtal12b,
  BrisEtal02, EtniEtal06, BassSuzu17}.
